Quantum H theorem, variational entropy, and relaxation processes

### 2020-12-16 tex/relaxproc.tex
Typos, 1st intro paragraph, secs. 2.0, 2.1

  \section{Relaxation processes in degenerated quantum gases}
Consider that the distribution function $f_{nM}$ is a function of the local number of particles $\mathcal{N}_M$, the local number of particles in a quantum energy state $\mathcal{N}_{M}^{n}$ and the time $t$ as follow
\begin{equation}
    f=f(\mathcal{N}_M,\mathcal{N}_M^{n},t),
\end{equation}
where $\mathcal{N}_{M}^{n}$ is defined as
\begin{equation}
    \mathcal{N}_{M}^{n}= f_{nM} \delta \epsilon_n.
\end{equation}
Besides the local number of particles is a function of time $\mathcal{N}_J=\mathcal{N}_J(t)$ and the local number of particles in a quantum energy state is a function of time and the local number of particles $\mathcal{N}_J^{j}=\mathcal{N}_J^{j}(\mathcal{N}_M,t)$. This is due to when a cell transfer particles to another cell, the particles in some defined state energy levels must change.\\
In order to obtain the analogous transport equation to this system, we apply the variation method to the functional $\Ss$. Due to $\Ss$ in equilibrium is proportional to entropy, and therefore a maximum, the variation must be zero. Then the equation of motion is
\begin{equation}
    0=\sum_{M=1}^{K} \sum_n \ln \left[ \frac{f_{nM}}{1\mp f_{nM}} \right] \left[ \frac{\partial f_{nM}}{\partial t}+\frac{\partial f_{nM}}{\partial \mathcal{N}_J}\dot{\mathcal{N}}_J+\frac{\partial f_{nM}}{\partial \mathcal{N}_J^{j}}\left( \frac{\partial \mathcal{N}_J^{j}}{\partial t}+\frac{\partial \mathcal{N}_J^{j}}{\partial \mathcal{N}_L}\dot{\mathcal{N}}_L \right) \right]. \label{transportequation1}
\end{equation}
This equation is valid in equilibrium. When the system is out of equilibrium, the variation is different from zero. Due to this, an expression has to be included in (\ref{transportequation1}). This term, in analogy to the Boltzmann transport equation, will be the collision term and will be expressed as $\left( \frac{df_{nM}}{dt} \right)_{coll}$. Moreover, we propose that this term contributes to the equation of motion per each cell.\footnote{The collision term is only in a defined cell and local group of energy. If we are describing the total system, we need to include all contributions (each cell and energy group).} Therefore, (\ref{transportequation1}) casts into
\begin{eqnarray}
    \sum_{M=1}^{K}\sum_n \left( \frac{df_{nM}}{dt} \right)_{coll}&=&\sum_{M=1}^{K} \sum_n \ln \left[ \frac{f_{nM}}{1\mp f_{nM}} \right] \nonumber \\
    &&\times \left[ \frac{\partial f_{nM}}{\partial t}+\frac{\partial f_{nM}}{\partial \mathcal{N}_J}\dot{\mathcal{N}}_J+\frac{\partial f_{nM}}{\partial \mathcal{N}_J^{j}}\left( \frac{\partial \mathcal{N}_J^{j}}{\partial t}+\frac{\partial \mathcal{N}_J^{j}}{\partial \mathcal{N}_L}\dot{\mathcal{N}}_L \right) \right].  \nonumber \\ \label{transportequation2}
\end{eqnarray}
The equation (\ref{transportequation2}) is the time evolution equation to a quantum ideal gas. \\

>>>>

  \section{Relaxation processes in degenerated quantum gases}\label{sec:relaxproc}
Consider that the distribution function $f_{nM}$ is a function of the local number of particles $\mathcal{N}_M$, the local number of particles in a quantum energy state $\mathcal{N}_{M}^{n}$ and the time $t$ as follow
\begin{equation}
    f=f(\mathcal{N}_M,\mathcal{N}_M^{n},t),
\end{equation}
where $\mathcal{N}_{M}^{n}$ is defined as
\begin{equation}
    \mathcal{N}_{M}^{n}= f_{nM} \delta \epsilon_n.
\end{equation}
Besides the local number of particles is a function of time $\mathcal{N}_J=\mathcal{N}_J(t)$ and the local number of particles in a quantum energy state is a function of time and the local number of particles $\mathcal{N}_J^{j}=\mathcal{N}_J^{j}(\mathcal{N}_M,t)$. This is due to when a cell transfer particles to another cell, the particles in some defined state energy levels must change.\\
In order to obtain the analogous transport equation to this system, we apply the variation method to the functional $\Ss$. Due to $\Ss$ in equilibrium is proportional to entropy, and therefore a maximum, the variation must be zero. Then the equation of motion is
\begin{equation}
    0=\sum_{M=1}^{K} \sum_n \ln \left[ \frac{f_{nM}}{1\mp f_{nM}} \right] \left[ \frac{\partial f_{nM}}{\partial t}+\frac{\partial f_{nM}}{\partial \mathcal{N}_J}\dot{\mathcal{N}}_J+\frac{\partial f_{nM}}{\partial \mathcal{N}_J^{j}}\left( \frac{\partial \mathcal{N}_J^{j}}{\partial t}+\frac{\partial \mathcal{N}_J^{j}}{\partial \mathcal{N}_L}\dot{\mathcal{N}}_L \right) \right]. \label{transportequation1}
\end{equation}
This equation is valid in equilibrium. When the system is out of equilibrium, the variation is different from zero. Due to this, an expression has to be included in (\ref{transportequation1}). This term, in analogy to the Boltzmann transport equation, will be the collision term and will be expressed as $\left( \frac{df_{nM}}{dt} \right)_{coll}$. Moreover, we propose that this term contributes to the equation of motion per each cell.\footnote{The collision term is only in a defined cell and local group of energy. If we are describing the total system, we need to include all contributions (each cell and energy group).} Therefore, (\ref{transportequation1}) casts into
\begin{eqnarray}
    \sum_{M=1}^{K}\sum_n \left( \frac{df_{nM}}{dt} \right)_{coll}&=&\sum_{M=1}^{K} \sum_n \ln \left[ \frac{f_{nM}}{1\mp f_{nM}} \right] \nonumber \\
    &&\times \left[ \frac{\partial f_{nM}}{\partial t}+\frac{\partial f_{nM}}{\partial \mathcal{N}_J}\dot{\mathcal{N}}_J+\frac{\partial f_{nM}}{\partial \mathcal{N}_J^{j}}\left( \frac{\partial \mathcal{N}_J^{j}}{\partial t}+\frac{\partial \mathcal{N}_J^{j}}{\partial \mathcal{N}_L}\dot{\mathcal{N}}_L \right) \right].  \nonumber \\ \label{transportequation2}
\end{eqnarray}
The equation (\ref{transportequation2}) is the time evolution equation to a quantum ideal gas. \\
